### 2015-04-30 rscripts/data_review.Rmd
revising data review

```{r, echo=FALSE}
source("munging.R")
breakoutDays(censor.dt[,
  user_id := .GRP, by=user_id
][,
  location_id := .GRP, by=location_id
][,
  run_id := 0
][,
  sample_id := 0
][,
  target := FALSE
])
setkey(censor.dt, run_id, sample_id, login_day, login_time, logout_day, logout_time, user_id, location_id)

@@

```{r, echo=FALSE}
limits.dt <- censor.dt[,list(first=min(login), last=max(logout)), keyby=location_id]
limits.dt
save(censor.dt, limits.dt, file = "../input/censored.Rdata")
```

@@

>>>>

```{r, echo=FALSE}
source("munging.R")
breakoutDays(censor.dt[,
  user_id := .GRP, by=user_id
][,
  location_id := .GRP, by=location_id
])
setkey(censor.dt, login_day, login_time, logout_day, logout_time, user_id, location_id)
censor.dt
```

@@

```{r, echo=FALSE}
## TODO switch to log(in|out) day
limits.dt <- censor.dt[,list(first=min(login), last=max(logout)), keyby=location_id]
limits.dt
save(censor.dt, limits.dt, file = "../input/censored.Rdata")
```

The locations have different patterns of activity, reflecting their different hours of operation.

@@

hours.dt <- censor.dt[,
  list(login_day, login_time, logout_day, logout_time, logout_time_adj=0),
  keyby=list(location_id, user_id)
]
hours.dt[ login_day != logout_day,
   logout_time_adj := logout_time + 24*60*60
]
hours.dt <- hours.dt[,
  list(open=min(login_time), close=max(logout_time, logout_time_adj)),
  by=list(login_day, location_id)
]
p <- ggplot(hours.dt[,
  list(med_open = median(open), med_close=median(close)), by=location_id
][, open_id:=.GRP, by=list(med_open, location_id)])+aes(x=open_id, y=med_open/3600) + geom_point() + geom_hline(yintercept=1:23, color="red") + theme_bw()
